Using reference models in variable selection \vspace{.1in}

### 2020-02-08 paper/ref_approach.tex

\begin{center}
\begin{algorithm}[H]
\SetAlgoLined
\KwResult{$R:=\{\text{selected variables}\}$}
 $F:=\{\text{set of variables}\}$ \;
 $R=\{\emptyset\}$ \;
 Fit reference model\;
 \While{$F\neq\{\emptyset\}$}{
   projection.HeuristicSearch \;
   projection.elpdEstimate() \;
%:
   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{base}}>0)\geq\alpha)$\} \;

@@

>>>>

\begin{center}
\begin{algorithm}[H]
\SetAlgoLined
\KwResult{$R:=\{\text{selected variables}\}$}
 $F:=\{\text{set of variables}\}$ \;
 $R=\{\emptyset\}$ \;
 Fit reference model\;
 \While{$F\neq\{\emptyset\}$}{
   projection.HeuristicSearch() \;
   projection.elpdEstimate() \;
%:
   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{base}}>0)\geq\alpha)$\} \;

@@

In the experiments shown in the next sections, we include an additional iterative
method which we refer to as 'iterative lasso'. It consists of the same iterative
algorithm as iterative projpred expect for not using any reference model but
the lasso method for variable selection, instead.
That is, it uses the observed target values instead of predictions of the reference model.
Iterative lasso can help to distangle the effects
of the iterative procedure and the usage of a reference model in complete feature selection.
